\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-05 rebuttal.tex

\begin{itemize}

    \item \emph{For longer journal articles, a citation style like 'apalike' that uses the
author names in the references would be more pleasant to read since it saves
reviewers from jumping back and forth all the time.}

As indicated by the Editor in Chief, we need to keep the current citation style.

    \item \emph{p9: Instead of storing these models separately (having to
    update each
of them), wouldn't it be easier to compute them once they are needed, and
to maintain a quasi-global world belief?} This is a design choice that trades
off scalability for complete domain explicitation. We have clarified and
justified this design choice in section 2.2 (\emph{Knowledge model}). Also, in
the specific case of agent-dependent models, we want to represent
false-beliefs situations (where one agent carries wrong beliefs on the world)
that can typically not be computed ``on demand'' because they are observable
only in specific situations.

@@

    \item \emph{p10 l 49: How is this discrimination done?} The discrimination
        algorithms are detailed in \cite{Ros2010b} (Best Paper Award at
        ROMAN2010). We have added a reference to this paper.

    \item \emph{p15 While the production of such rules is one thing, managing the
    dynamics of this knowledge and e.g. removing it once it's outdated or updating
once it has changed are crucial. This should be explained in more detail.}
The dynamics of the knowledge are managed by the clients (ie, the deliberative
components like the situation assessment module, the dialogue processing module,
etc.) of the knowledge base themselves. In particular, the situation assessment
module recomputes at every step the whole set of spatial relations, and update
accordingly the knowledge base. This has been clarified in both section 2.2
(\emph{Knowledge model}) and section 3.2 (\emph{Situation Assessment, Human
Awareness, Perspective Taking})

    \item \emph{The example scenarios have very bold names for often rather
        simple things.} The reviewer is indeed right. We have mistakenly used internal
        \emph{code names} for the experiments' names. These have been reworded.

    \item \emph{p 20: AFAIK KnowRob stores OWL as facts in Prolog, why
        should the TBOX be immutable?} The reviewer is right insofar as there is
        not limitations inherent to Prolog in that regard. We have removed the
        reference to KnowRob TBOX, that originated in a discussion with KnowRob's author who told
        us then that KnowRob could not update at run-time its TBox. Since we were
        not able to find litterature confirming this fact, it is likely better
        not to mention it.

\end{itemize}

@@

\begin{itemize}
    \item \emph{pg 10 (section 3.2.1)
            "The system supports ...". This is one example of a topic that would
            be really interesting to the readers and it is just hinted. In
            particular, learning rules like "cats are animals" maybe really
            nice, but are such rules compatible with the existing knowledge?
            Adding them as triples may work only in absence of contradictions} The
            various natural language grounding processes that are made possible
            within this semantic
            architecture would require a relatively long discussion to be adequately
            explained. They are besides already presented in~\cite{Lemaignan2011a}.
            We have added an explicit reference to this previous publication.

            To specifically answer the reviewer question on how possible
            contradictions are managed, we indeed check that new statements proposed
            by the human do not lead to contradictions before inserting them.

    \item \emph{pg 10 (section 3.2.1)
            "Note that, while the system benefits from the complementary
            modalities, they are not all
            required. The dialogue system can run with only the verbal modality,
            at the cost of a simpler interaction."
        Possibly true, but unjustified claim.} An example has been added to
        clarify this fall-back mechanism.

    \item \emph{"The second level of integration of multi-modality is implicit:
            by computing symbolic properties 
            from the geometry, richer descriptions and hence discrimination
            possibilities are available: 
            for instance, if reachability is available, the robot may ask "do
            you mean the bottle that is 
            accessible to me?" to discriminate between the three bottles. That
            way, procedures relying on 
            discrimination transparently benefit from added modalities." Concept
            remains unclear.} The paragraph has been rephrased and the example
            updated to clarify the concepts.

    \item \emph{In the current form, Section 2.3 seems outside the scope of the
            paper. The discussion on working memory is quite interesting, but
            since it is still to be developed in detail it maybe a topic for
            future perspectives. In that case it would be nice to read which AI
            techniques could help tackling the issue.} The presentation of
            ``internal cognitive skills'' has been extended, refined and integrated
            to section 3. Specifically, several litterature references have been
            added to the discussion on memory, both on the theoritical side and on
            existing implementations.

    \item \emph{``Subclasses (like Give, LookAt, etc.) are not asserted in the
            common-sense ontology, but are added by the execution controller (in
            link with the symbolic task planner) and the natural language
            processor based on what is actually performable and/or
            understandable by the robot at run-time'' This is very difficult to
            understand. Provide more details and, possibly, an example} The paragraph
            has been rephrased and illustrated to be easier to understand.

\end{itemize}

### 2014-05-05 paper.tex
Moved the 'key issues' stub to the discussion
Clarify what 'cognitive skills' are + style of intro sec 3

TDB

@@

While the previous section provided an overview of our cognitive architecture,
as well as its associated knowledge model, this section discuss each of its main
``building blocks'' that we each consider to instantiate different cognitive
skills. Since each of these components have multiple connections to the others,
no obvious presentation order stands out, and the reader may have to rely on
Figure~\ref{fig|archi} as a guide.

We start by discussing the main \emph{internal} cognitive capabilities,
implemented in the knowledge base itself, and then discuss successively {\sc
Spark}, the situation assessment module, {\sc Dialogs}, the dialogue processor,
HATP, the symbolic task planner, and finally the main features of our execution
controllers.

@@

We call \emph{internal} those cognitive capabilities that are tightly bound to
the knowledge model, and hence implemented directly inside {\sc Oro}, the knowledge base.
We present here three of them, \emph{reasoning}, \emph{theory of mind} modeling
and our (naive) approach to \emph{memory management}.

@@

>>>>

@@

While the previous section provided an overview of our cognitive architecture
as well as its associated knowledge model, this section discusses each of its main
``building blocks''. Each of these components may have connections to several
others, and we invite the reader to refer to Figure~\ref{fig|archi} as a guide
if needed.

\begin{inparaenum} In our context, we call \emph{cognitive skills} the
deliberative behaviours that are \item \emph{stateful} both in terms of
\emph{time} (keeping track of previous states is required for the component
to perform adequately) and \emph{modalities} (for instance, \emph{situated}
dialogue requires interleaving different communication modalities), \item
manipulate \emph{explicit semantics}, typically by the mean of symbolic
reasoning, \item operate at the \emph{human-level}, \ie are legible to the
humans, typically by acting at similar levels of abstraction.\end{inparaenum}

We start by discussing first the main \emph{internal} cognitive capabilities,
implemented in the knowledge base itself, and then discuss successively the
situation assessment module {\sc Spark}, the dialogue processor {\sc Dialogs},
the symbolic task planner HATP, and finally the main features of our execution
controllers.

@@

We call \emph{internal} those cognitive capabilities that are tightly bound to
the knowledge model, and hence implemented directly within the {\sc Oro} server.
We present here three of them: \emph{reasoning}, \emph{theory of mind} modeling
and our (naive) approach to \emph{memory management}.

@@

We would like first to restate the main challenges to artificial intelligence
raised by human-robot interaction.

\fxfatal{TDB}
